\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage[inline]{trackchanges}

\usepackage{url}
\urldef{\mails}\path|{claas.wilke, michael.thiele, c.wende}@inf.tu-dresden.de|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

% For german character ä,ö,ü,ß
\usepackage[latin1]{inputenc}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed

\title{Defining and Interpreting OCL Constraints on Arbitrary Models and Model
Instances \note{the term model instance is not very common and easy to distinguish from
model. What do you think of model implementations?}}

% a short form should be given in case it is too long for the running head
\titlerunning{Defining and Interpreting OCL on Arbitrary Models and Model Instances}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Claas Wilke\and Michael Thiele\and Christian Wende\\
\mails}
%
\authorrunning{Defining and Interpreting OCL on Arbitrary Models and Model Instances}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Technische Universität Dresden\\
Department of Computer Science\\
Institute for Software and Multimedia Technology\\
Software Technology Group
%\url{http://www.st.inf.tu-dresden.de}
}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle

\note{do we use british or american english?}
\begin{abstract}
In recent years the Object Constraint Language (OCL) has become a popular 
constraint language that is used \change{on top of}{in combination with}
multiple modeling languages such as UML, EMF Ecore and various domain specific 
languages. \remove{OCL is only loosely coupled to these modeling languages, }It
is rather common to reuse the same OCL parsers for multiple different modeling 
languages. 
\change{While OCL-annotated models are implemented and instantiated in various
implementation languages, dynamic OCL semantics as required for OCL constraint 
interpretation is typically bound to a specific implementation language.} 
In this paper, we propose an architecture for an OCL tool that
\change{encapsulates}{hides} meta-models, models and model
\change{instances in specific implementation languages} behind well-defined
interfaces. We present an OCL interpreter that can interpret OCL constraints 
on various different model \change{instantiations}{implementations} and
\change{provides}{, thus, enables} reuse of the same dynamic OCL semantics
implementation for all these \change{instantiation types}{implementation types}.
The architecture is evaluated \change{by presenting}{in} three case studies
defining and interpreting OCL constraints on multiple models and model
\change{instances}.

\keywords{OCL, MDSD, Modeling, Constraint Interpretation.}
\end{abstract}

  \input{chapters/introduction}
   
  \input{chapters/foundations}

  \input{chapters/implementation}

  \input{chapters/casestudies}
  
  \input{chapters/relatedwork}

  \input{chapters/conclusion} 

  \bibliographystyle{alpha}
  \bibliography{models2010}  

\end{document}
